First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-08-04 ms.tex
Updated some references

Future iterations of this model will contain a spectral index 
and multiple polarization components.
\textbf{E.}~Lenc, et al. (in review) demonstrated the presence of strong polarized large-scale structures 
in the EoR0 field at 154 MHz with varying Faraday depths. They observed rotations in the
Stokes Q--U plane due to ionospheric conditions, which will need to be taken into account
in our future diffuse models.

@@

\textbf{Diffuse emission model.} The diffuse model here contained no spectral information
and represented only the Stokes I polarization. Nevertheless subtracting this model removed
90\% of the residual power in the foreground wedge. Adding a spectral index and multiple
polarization components to the model will improve this subtraction even further.
As \textbf{E.}~Lenc, et al. 2016 (in review) demonstrated, substantial polarized diffuse structure
exists in the EoR0 field. The contributions to Stokes Q and U depend on the ionospheric
conditions, which will be accounted for in future analyses to appropriately model this
emission. 
In addition the diffuse model will be extended to an all-sky model. It is evident from the
jackknives shown in Figure~\ref{fig:jackknife} that strong emission near the horizon is
leaking into our power spectra during off-zenith observations. By modeling and subtracting
this emission we may be able to recover these observations in future analyses.

>>>>

Future iterations of this model will contain a spectral index 
and multiple polarization components.
\textbf{\citet{Lenc:2016}} demonstrated the presence of strong polarized large-scale structures 
in the EoR0 field at 154 MHz with varying Faraday depths. They observed rotations in the
Stokes Q--U plane due to ionospheric conditions, which will need to be taken into account
in our future diffuse models.

@@

\textbf{Diffuse emission model.} The diffuse model here contained no spectral information
and represented only the Stokes I polarization. Nevertheless subtracting this model removed
90\% of the residual power in the foreground wedge. Adding a spectral index and multiple
polarization components to the model will improve this subtraction even further.
As \textbf{\citet{Lenc:2016}} demonstrated, substantial polarized diffuse structure
exists in the EoR0 field. The contributions to Stokes Q and U depend on the ionospheric
conditions, which will be accounted for in future analyses to appropriately model this
emission. 
In addition the diffuse model will be extended to an all-sky model. It is evident from the
jackknives shown in Figure~\ref{fig:jackknife} that strong emission near the horizon is
leaking into our power spectra during off-zenith observations. By modeling and subtracting
this emission we may be able to recover these observations in future analyses.
